Music Perception: Stimuli profiles (2sd)

### 2021-01-21 material/expstimuli/selection/analysis(2sd).Rmd
add analysis 2sd
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Note: SubNr 8 was excluded due to an experimental error, SubNr 16 was excluded due to a deviated tempo (see analysis for [teaching-v1.0](https://github.com/atsukotominaga/teaching-v1.0))

@@

## Plots
### Articulation
```{r ioi_art_plot, echo = FALSE}
p_ioi_art <- ggplot(ioi[Skill == "articulation"], aes(x = Instance, y = Mean, fill = Condition)) +
 geom_bar(stat = "identity", position = position_dodge()) +
 geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
               width = .2, position = position_dodge(.9)) +
 geom_hline(yintercept = 188, linetype = "dashed") +
 scale_x_continuous(breaks = seq(1:24)) +
 labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Articulation)")
p_ioi_art

p_ioi_art_all <- ggplot(ioi_art, aes(x = Skill, y = Mean, fill = Condition)) +
   geom_bar(stat = "identity", position = position_dodge()) +
   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                 width = .2, position = position_dodge(.9)) +
   geom_hline(yintercept = 188, linetype = "dashed") +
   labs(y = "IOI (ms)", subtitle = "IOI: Averaged (Articulation)")
p_ioi_art_all
```
### Dynamics
```{r ioi_dyn_plot, echo = FALSE}
p_ioi_dyn <- ggplot(ioi[Skill == "dynamics"], aes(x = Instance, y = Mean, fill = Condition)) +
 geom_bar(stat = "identity", position = position_dodge()) +
 geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
               width = .2, position = position_dodge(.9)) +
 geom_hline(yintercept = 188, linetype = "dashed") +
 scale_x_continuous(breaks = seq(1:24)) +
 labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Dynamics)")
p_ioi_dyn

@@

## Plots
```{r kot_plot, echo = FALSE}
p_kot <- ggplot(kot, aes(x = Instance, y = Mean, fill = Condition)) +
   geom_bar(stat = "identity", position = position_dodge()) +
   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                 width = .2, position = position_dodge(.9)) +
   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
   labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation)")
p_kot

@@

@@

## Plots
```{r vel_plot, echo = FALSE}
p_vel <- ggplot(vel, aes(x = Instance, y = Mean, fill = Condition)) +
   geom_bar(stat = "identity", position = position_dodge()) +
   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                 width = .2, position = position_dodge(.9)) +
   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
   labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics)")
p_vel

@@

## Plots
```{r vel_diff_plot, echo = FALSE}
p_vel_diff <- ggplot(vel_diff, aes(x = Instance, y = Mean, fill = Condition)) +
geom_bar(stat = "identity", position = position_dodge()) +
geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
              width = .2, position = position_dodge(.9)) +
facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
labs(y = "KV difference", subtitle = "KV-Diff: Each instance (Dynamics)")
p_vel_diff

@@

>>>>

Note: SubNr 8 was excluded due to an experimental error, SubNr 16 was excluded due to a deviated tempo (see analysis for [music-teaching: experiment-1](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-1))

@@

## Plots
### Articulation
```{r ioi_art_plot, echo = FALSE}
p_ioi_art_t <- ggplot(ioi[Skill == "articulation" & Condition == "teaching"], aes(x = Instance, y = Mean)) +
 geom_bar(stat = "identity", position = position_dodge()) +
 geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
               width = .2, position = position_dodge(.9)) +
 geom_hline(yintercept = 188, linetype = "dashed") +
 scale_x_continuous(breaks = seq(1:24)) +
 labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Articulation-Teaching)")
p_ioi_art_t

p_ioi_art_p <- ggplot(ioi[Skill == "articulation" & Condition == "performing"], aes(x = Instance, y = Mean)) +
 geom_bar(stat = "identity", position = position_dodge()) +
 geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
               width = .2, position = position_dodge(.9)) +
 geom_hline(yintercept = 188, linetype = "dashed") +
 scale_x_continuous(breaks = seq(1:24)) +
 labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Articulation-Performing)")
p_ioi_art_p

p_ioi_art_all <- ggplot(ioi_art, aes(x = Skill, y = Mean, fill = Condition)) +
   geom_bar(stat = "identity", position = position_dodge()) +
   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                 width = .2, position = position_dodge(.9)) +
   geom_hline(yintercept = 188, linetype = "dashed") +
   labs(y = "IOI (ms)", subtitle = "IOI: Averaged (Articulation)")
p_ioi_art_all
```
### Dynamics
```{r ioi_dyn_plot, echo = FALSE}
p_ioi_dyn_t <- ggplot(ioi[Skill == "dynamics" & Condition == "teaching"], aes(x = Instance, y = Mean)) +
 geom_bar(stat = "identity", position = position_dodge()) +
 geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
               width = .2, position = position_dodge(.9)) +
 geom_hline(yintercept = 188, linetype = "dashed") +
 scale_x_continuous(breaks = seq(1:24)) +
 labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Dynamics)")
p_ioi_dyn_t

p_ioi_dyn_p <- ggplot(ioi[Skill == "dynamics" & Condition == "performing"], aes(x = Instance, y = Mean)) +
 geom_bar(stat = "identity", position = position_dodge()) +
 geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
               width = .2, position = position_dodge(.9)) +
 geom_hline(yintercept = 188, linetype = "dashed") +
 scale_x_continuous(breaks = seq(1:24)) +
 labs(y = "IOI (ms)", subtitle = "IOI: Each instance (Dynamics)")
p_ioi_dyn_p

@@

@@

## Plots
```{r kot_plot, echo = FALSE}
p_kot_a <- ggplot(kot[Condition == "teaching"], aes(x = Instance, y = Mean)) +
   geom_bar(stat = "identity", position = position_dodge()) +
   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                 width = .2, position = position_dodge(.9)) +
   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
   labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation-Teaching)")
p_kot_a

p_kot_d <- ggplot(kot[Condition == "performing"], aes(x = Instance, y = Mean)) +
   geom_bar(stat = "identity", position = position_dodge()) +
   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                 width = .2, position = position_dodge(.9)) +
   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
   labs(y = "KOT (ms)", subtitle = "KOT: Each instance (Articulation-Performing)")
p_kot_d

@@

## Plots
```{r vel_plot, echo = FALSE}
p_vel_t <- ggplot(vel[Condition == "teaching"], aes(x = Instance, y = Mean)) +
   geom_bar(stat = "identity", position = position_dodge()) +
   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                 width = .2, position = position_dodge(.9)) +
   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
   labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics-Teaching)")
p_vel_t

p_vel_p <- ggplot(vel[Condition == "performing"], aes(x = Instance, y = Mean)) +
   geom_bar(stat = "identity", position = position_dodge()) +
   geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                 width = .2, position = position_dodge(.9)) +
   facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
   labs(y = "Key Velocity", subtitle = "KV: Each instance (Dynamics-Performing)")
p_vel_p

@@

## Plots
```{r vel_diff_plot, echo = FALSE}
p_vel_diff_t <- ggplot(vel_diff[Condition == "teaching"], aes(x = Instance, y = Mean)) +
geom_bar(stat = "identity", position = position_dodge()) +
geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
              width = .2, position = position_dodge(.9)) +
facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
labs(y = "KV difference", subtitle = "KV-Diff: Each instance (Dynamics)")
p_vel_diff_t

p_vel_diff_p <- ggplot(vel_diff[Condition == "performing"], aes(x = Instance, y = Mean)) +
geom_bar(stat = "identity", position = position_dodge()) +
geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
              width = .2, position = position_dodge(.9)) +
facet_grid(Subcomponent ~ .) + scale_x_continuous(breaks = seq(1:24)) +
labs(y = "KV difference", subtitle = "KV-Diff: Each instance (Dynamics)")
p_vel_diff_p

@@

# Pilot data (with 9 participants)
```{r read-2, include = FALSE}
order_data <- fread("../../../analysis/order_data.txt")
```

order stimuli by participants' performance (left: low accuracy - high: high accuracy)

## Legato
```{r kot-legato, echo = FALSE}
# kot-legato
kot_legato <- kot[Subcomponent == "Legato"]
order_art <- order_data[technique == "articulation"]
order_art <- order_art[order(condition, item)]

kot_legato$Correct <- 0
kot_legato[Condition == "teaching"]$Correct <- order_art[condition == "teaching"]$mean_percent
kot_legato[Condition == "performing"]$Correct <- order_art[condition == "performing"]$mean_percent

ggplot(kot_legato[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Teaching-Legato (Correct Answer = YES)")

ggplot(kot_legato[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Performing-Legato (Correct Answer = NO)")
```

## Staccato
```{r kot-staccato, echo = FALSE}
# kot-staccato
kot_staccato <- kot[Subcomponent == "Staccato"]

kot_staccato$Correct <- 0
kot_staccato[Condition == "teaching"]$Correct <- order_art[condition == "teaching"]$mean_percent
kot_staccato[Condition == "performing"]$Correct <- order_art[condition == "performing"]$mean_percent

ggplot(kot_staccato[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Teaching-Staccato (Correct Answer = YES)")

ggplot(kot_staccato[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Performing-Staccato (Correct Answer = NO)")
```

## Legato vs. Staccato
```{r leg-sta, echo = FALSE}
leg_sta <- rbind(kot_legato, kot_staccato)

ggplot(leg_sta[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Teaching (Correct Answer = YES)")

ggplot(leg_sta[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KOT (ms)", subtitle = "Performing (Correct Answer = NO)")
```

## Forte
```{r vel-forte, echo = FALSE}
# vel-forte
vel_forte <- vel[Subcomponent == "Forte"]
order_dyn <- order_data[technique == "dynamics"]
order_dyn <- order_dyn[order(condition, item)]

vel_forte$Correct <- 0
vel_forte[Condition == "teaching"]$Correct <- order_dyn[condition == "teaching"]$mean_percent
vel_forte[Condition == "performing"]$Correct <- order_dyn[condition == "performing"]$mean_percent

ggplot(vel_forte[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-Forte (Correct Answer = YES)")

ggplot(vel_forte[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-Forte (Correct Answer = NO)")
```

## Piano
```{r vel-piano, echo = FALSE}
# vel-piano
vel_piano <- vel[Subcomponent == "Piano"]

vel_piano$Correct <- 0
vel_piano[Condition == "teaching"]$Correct <- order_dyn[condition == "teaching"]$mean_percent
vel_piano[Condition == "performing"]$Correct <- order_dyn[condition == "performing"]$mean_percent

ggplot(vel_piano[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-Piano (Correct Answer = YES)")

ggplot(vel_piano[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-Piano (Correct Answer = NO)")
```

## Forte vs. Piano
```{r for-pia, echo = FALSE}
for_pia <- rbind(vel_forte, vel_piano)

ggplot(for_pia[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching (Correct Answer = YES)")

ggplot(for_pia[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing (Correct Answer = NO)")
```

## Forte to Piano
```{r vel-diff-ftop, echo = FALSE}
# vel_diff-ftop
vel_diff_ftop <- vel_diff[Subcomponent == "FtoP"]

vel_diff_ftop$Correct <- 0
vel_diff_ftop[Condition == "teaching"]$Correct <- order_dyn[condition == "teaching"]$mean_percent
vel_diff_ftop[Condition == "performing"]$Correct <- order_dyn[condition == "performing"]$mean_percent

ggplot(vel_diff_ftop[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-FtoP (Correct Answer = YES)")

ggplot(vel_diff_ftop[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-FtoP (Correct Answer = NO)")
```

## Piano to Forte
```{r vel-diff-ptof, echo = FALSE}
# vel_diff-ptof
vel_diff_ptof <- vel_diff[Subcomponent == "PtoF"]

vel_diff_ptof$Correct <- 0
vel_diff_ptof[Condition == "teaching"]$Correct <- order_dyn[condition == "teaching"]$mean_percent
vel_diff_ptof[Condition == "performing"]$Correct <- order_dyn[condition == "performing"]$mean_percent

ggplot(vel_diff_ptof[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching-PtoF (Correct Answer = YES)")

ggplot(vel_diff_ptof[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing-PtoF (Correct Answer = NO)")
```

## FtoP vs. PtoF
```{r ftop-ptof, echo = FALSE}
ftop_ptof <- rbind(vel_diff_ftop, vel_diff_ptof)

ggplot(ftop_ptof[Condition == "teaching"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Teaching (Correct Answer = YES)")

ggplot(ftop_ptof[Condition == "performing"], aes(x = reorder(Instance, Correct), y = Mean, fill = Correct, color = Subcomponent)) + geom_bar(stat = "identity", position = position_dodge()) + geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .2, position = position_dodge(.9)) + labs(x = "Stimuli", y = "KV", subtitle = "Performing (Correct Answer = NO)")
```
